---
title: "set4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(fpp)
```

#### 2.The data below represent the monthly sales (in thousands) of product A for a plastics manufacturer for years 1 through 5 (data set plastics)

```{r}
data(plastics)
plastics
```

> (a) Plot the time series of sales of product A. Can you identify seasonal fluctuations and/or a
trend?

```{r}
plot(plastics)
```

Temos uma trend que está aumentando conforme os anos e uma sazonalidade anual.

> (b) Use an STL decomposition to calculate the trend-cycle and seasonal indices. (Experiment with having fixed or changing seasonality.)

```{r}
plastics.fit <- stl(plastics, s.window="periodic")
plot(plastics.fit)
plastics.fit <- stl(plastics, s.window=5)
plot(plastics.fit)
plastics.fit <- stl(plastics, s.window=7)
plot(plastics.fit)
```

Restos e trend sofreram grandes alterações, mas qual o melhor?

> (c) Do the results support the graphical interpretation from part (a)?

Sim!

> (d) Compute and plot the seasonally adjusted data

```{r}
plastics.fit.adj <- seasadj(plastics.fit)
plot(plastics.fit.adj)
```

> (e) Change one observation to be an outlier (e.g., add 500 to one observation), and recompute the seasonally adjusted data. What is the effect of the outlier

```{r} 
plastics2 <- plastics
plastics2[20] <- plastics2[10] + 500
plastics2.fit <- stl(plastics2, s.window="periodic")
plastics2.fit.adj <- seasadj(plastics2.fit)
plot(plastics2.fit.adj)
```

---

> (f) Does the outlier have an effect if you use robust=TRUE with the stl function?

```{r} 
plastics3 <- plastics
plastics3[20] <- plastics3[10] + 500
plastics3.fit <- stl(plastics3, s.window="periodic", robust=TRUE)
plastics3.fit.adj <- seasadj(plastics3.fit)
plot(plastics3.fit.adj)
```

Não (?)

> (g) Does it make any difference if the outlier is near the end rather than in the middle of the time series?

```{r} 
plastics3 <- plastics
plastics3[59] <- plastics3[59] + 500
plastics3.fit <- stl(plastics3, s.window="periodic", robust=TRUE)
plastics3.fit.adj <- seasadj(plastics3.fit)
plot(plastics3.fit.adj)
```

> (h) Use a random walk to produce forecasts of the seasonally adjusted data.

```{r} 
plot(naive(plastics.fit.adj))
```

> (i) Reseasonalize the results to give forecasts on the original scale.

```{r} 
plastics.fcast <- forecast(plastics.fit, method="naive")
plot(plastics.fcast)
```